### 2013-09-08 main.tex
splitting pystruct file
polish SZLJSP algorithm listing
convergence rates, citations, mehr todos fertig...
intermediate
start going on about stupid datasets
removed dataset blabla, maybe in appendix. added contained papers to the intro.
zusammenfassung/abstract.

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{pslatex}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}
\usepackage[urw-garamond]{mathdesign}
\usepackage{garamondx}
\usepackage{xspace}
\onehalfspacing
\KOMAoptions{DIV=last}

@@

@@

\newtheorem{corollary}{Corollary}
\newtheorem{corollarya}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{theorema}{Theorem}

@@

\tableofcontents
\end{spacing}
%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
\chapter*{Abstract}

@@

@@

\include{pystruct/paper}

>>>>

\usepackage{hyperref}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{refstyle}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{multicol}
%\usepackage{pslatex}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{mdwlist}
\usepackage{url}
\usepackage[noend]{algpseudocode}
\usepackage[small]{caption}
\usepackage{setspace}
\usepackage{color}
\usepackage{minted}

%\usepackage{tgpagella}
%\usepackage[T1]{fontenc}

%\usepackage{garamondx}
%\usepackage[urw-garamond]{mathdesign}
\usepackage{xspace}
\onehalfspacing
\KOMAoptions{DIV=last}

@@

\makeatletter
\let\OldStatex\Statex
\renewcommand{\Statex}[1][3]{%
\setlength\@tempdima{\algorithmicindent}%
\OldStatex\hskip\dimexpr#1\@tempdima\relax}
\makeatother

@@

%\newtheorem{corollary}{Corollary}
%\newtheorem{corollarya}{Corollary}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}
%\newtheorem{theorema}{Theorem}

@@

\tableofcontents
\end{spacing}
%\listoffigures
%\listoftables
\chapter*{Zusammenfassung}
Automatische Segementierung und Erkennung von semantischen Klassen in
natuerlichen Bildern ist ein wichtiges offenes Problem des machinellen Sehens.
Einer der am weitest verbreiteten Ans\"atze zu dieser Aufgabe basiert auf
Conditional Random Fields und Verfahren der strukturierten Vorhersage. Die
Vorhersage f\"ur Modelle zur Bild-Markierung mittels Conditional Random Fields
ist f\"ur gew\"ohnlich nur approiximativ moeglich, bedingt d\"urch das
Vorhandensein von Kreisen in den zugrunde liegenden Nachbarschaftsgraphen.
Aus diesem Grund, und trotz der Beliebtheit von Conditional Random Field
Verfahren, ist das strukturierte Lernen f\"ur solche Anwendungen schlecht
verstanden.
%
Wir untersuchen verschiedene Lernalgorithmen in diesem
Zusammenhang. Wir zeigen, dass es m\"oglich ist trotz des Vorhandenseins von
Kreisen in den Nachbarschaftsgraphen exakte strukturierte Modelle zu lernen.
Wir stellen ausserdem eine Software-Bibliothek vor, die es erlaubt einen
weitreichenden Vergleich der besten Lernverfahren f\"ur strukturiertes Lernen
durchzuf\"uhren.
Unsere Studie erlaubt uns eine Charakterisation der betrachteten Algorithmen
in einer Reihe von Anwendungen, insbesondere der semantischen Segmentierung und
Objektklassensegmentierung.

\chapter*{Abstract}
Automatic segmentation and recognition of semantic classes in natural images is an important open problem in computer vision.
One of the most popular approaches to this task is based on conditional random fields and structured prediction.
For image labeling tasks, prediction using conditional random fields is usually only approximate, because of the presence
of loops of the neighborhood graph in the the image. Consequently, learning in
this setting is still little understood, despite the popularity of these
methods.
%
We investigate several learning algorithms in this setting. We show
how structured models can be learned exactly in practical settings, even in the
presence of many loops in the underlying neighborhood graphs.  We introduce a
software library that allows us to perform extensive empirical comparisons of
state-of-the-art structured learning approaches. This allows us to characterize
their practical properties in a range of applications, in particular for semantic segmentation
and object class segmentation.

@@

%\include{datasets/paper}

@@

\include{structured_prediction/paper}
\include{pystruct/paper}
